Search-Based Test Data Generation for JavaScript Functions with DOM

### 2018-01-25 doc/icse2018/icse2018.tex
Completed RQ1

\documentclass[sigconf]{acmart}

\usepackage{syntax}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{booktabs} % For formal tables
\usepackage{tikz}
\usetikzlibrary{arrows,shadows,positioning,decorations.pathmorphing}
\usepackage{pgf-umlsd}
\usepackage{tikz-uml}
\usepackage{hyperref}
\usepackage{upquote}
\usepackage{listings}
\usepackage{lsthaskell}
\usepackage{xspace}
\usepackage{algorithmic}
\usepackage{longtable}
\usepackage{subcaption}
\usepackage{pgfplots}
\pgfplotsset{compat=newest}
\usepackage[titlenotnumbered, linesnumbered, ruled]{algorithm2e} % language for algorithm description
\hypersetup{
  colorlinks   = true, %Colours links instead of ugly boxes
  urlcolor     = blue, %Colour for external hyperlinks
  linkcolor    = red, %Colour of internal links
  citecolor    = green %Colour of citations
}

@@

\newcommand{\Server}{\emph{Server}\xspace}
\newcommand{\Client}{\emph{Client}\xspace}
\newcommand{\User}{\emph{User}\xspace}
\newcommand{\Validator}{\emph{Validator}\xspace}
\newcommand{\thenBr}{\text{then}}
\newcommand{\elseBr}{\text{else}}
\newcommand{\inFor}{\text{inFor}}
\newcommand{\inWhile}{\text{while}}
\newcommand{\un}[1]{\underline{#1}}

@@

%Conference
\acmConference[ISSTA'18]{ACM SIGSOFT International Symposium on Software Testing and Analysis}{July 2018}{Amsterdam, The Netherlands} 
\acmYear{1997}
\copyrightyear{2016}

@@

\author{Alexander Elyasov}
\affiliation{%
  \institution{Utrecht University}
  \city{Utrecht} 
  \country{The Netherlands} 
}
\email{a.elyasov@uu.nl}

\author{Wishnu Prasetya}
\affiliation{%
  \institution{Utrecht University}
  \city{Utrecht} 
  \country{The Netherlands} 
}
\email{s.w.b.prasetya@uu.nl}

\author{Jurriaan Hage}
\affiliation{%
  \institution{Utrecht University}
  \city{Utrecht} 
  \country{The Netherlands} 
}
\email{j.hage@uu.nl}

@@

data Tag = HTML | HEAD | BODY | ...
type Context = CFlow | CMetadata | ...
data HtmlState = |c \label{ref.HtmlState.begin} |c
  HtmlState { depth      :: Int 
             , degree    :: Int    
             , ctx       :: Stack Context 
             , tagFreq   :: [(Int, Tag)] 
             , tags      :: [Tag]
             , ids       :: [String]
             , classes   :: [String] } |c \label{ref.HtmlState.end} |c
type GenState s = StateT s Gen |c \label{ref.GenState} |c
type GenHtmlState = GenState HtmlState Html |c \label{ref.GenHtmlState} |c
  \end{haskell}
  \caption{The \texttt{Arbitrary} instance for the \texttt{Html} data type}
  \label{fig.html.arb.def}
\end{figure}

@@

\begin{table}
  \caption{Genetic Algorithm Configurations}
  \label{tbl.gen.config}
    \scriptsize
  \begin{tabular}{l|r|r|r}
    \toprule
    \textbf{Parameter Name} & \textbf{R} & \textbf{G} & \textbf{G10} \\
    \hline
    Population size                   & 50  & 50  & 50  \\
    Archive size                      & 1   & 25  & 25  \\
    Maximum number of generations     & 200 & 200 & 200 \\
    Crossover rate                    & 0   & 0.5 & 0.5 \\
    Mutation rate                     & 0   & 0.5 & 0.5 \\
    History window size               & -   & -   & 10  \\
    \bottomrule
  \end{tabular}
\end{table}

@@

Table~\ref{tbl.case.studies} presents common quantitative characteristics for the selected case-studies. For each function, we reported the following metrics\footnote{\url{http://jsmeter.info/} is the tool used for measuring JS code statistics}: lines of code (\textbf{\#LOC}), number of branches (\textbf{\#BR}), depth (\textbf{\#D}), cyclomatic complexity (\textbf{CC}), halstead volume (\textbf{HV}) and maintainability index (\textbf{MI}). The four rightmost columns \textbf{DOM}, \textbf{id}, \textbf{tag} and \textbf{class} indicate if the function manipulates with the \emph{dom}, \emph{id}, \emph{tag} or \emph{class} respectively.

@@

\setlength\tabcolsep{0.8pt}

@@

  \caption{Performance statistics of branch coverage (in seconds) for four variations of the JS test generation framework}

@@

    \begin{tabular}{lc|ccc|ccc|ccc|ccc|ccc}

@@

      \multirow{2}{*}{\textbf{NAME}} & \multirow{2}{*}{\textbf{\#D}}         &  \multicolumn{3}{c|}{$m_r$} & \multicolumn{3}{c|}{$m_g$} & \multicolumn{3}{c|}{$m_{g10}$} & \multirow{2}{*}{$\frac{t_r}{t_g}$} &  \multirow{2}{*}{$\frac{t_r}{t_{g10}}$} & \multirow{2}{*}{$\frac{t_g}{t_{g10}}$}   & \multirow{2}{*}{r/g} &  \multirow{2}{*}{r/g10} & \multirow{2}{*}{g/g10} \\
      \cline{3-11}
            &                & $i$      & $t$  & $t/i$     & $i$& $t$&$t/i$             &$i$ &$t$ &$t/i$               &      &       &        &      &       &      \\
    \multicolumn{2}{l|}{\textbf{helpMe}*}     
                                 & 218      & 270  & 1.24      & 61 & 47 & 0.77             & 62 & 56 & 0.9                & 5.74 & 4.82  & 0.84   &      &      &       \\
    $(3,4,\inFor)$    & 1        & 4        & 4    & 1         & 5  & 3  & 0.6              & 8  & 6  & 0.75               & 1.33 & 0.67  & 0.5    & - & 0.39 & 0.37  \\
    $(5,6,\thenBr)$   & 2        & 4        & 5    & 1.25      & 8  & 6  & 0.75             & 7  & 5  & 0.71               & 0.83 & 1     & 1.2    & - & -  & -  \\
    $(5,15,\elseBr)$  & 2        & 121      & 156  & 1.29      & 24 & 21 & 0.86             & 23 & 24 & 1.04               & 7.43 & 6.5   & 0.88   & 0.87 & 0.86 & -  \\
    $(9,10,\thenBr)$  & 3        & 85       & 101  & 1.19      & 18 & 14 & 0.78             & 19 & 17 & 0.89               & 7.21 & 5.94  & 0.82   & 0.98 & 0.95 & -  \\
    $(9,14,\elseBr)$  & 3        & 4        & 4    & 1         & 6  & 4  & 0.67             & 5  & 4  & 0.8                & 1    & 1     & 1      & - & - & -  \\

@@

\multicolumn{2}{l|}{\textbf{isGameFinished}*} 
                                 & 264      & 220  & 0.83      & 32 & 30 & 0.94             & 43 & 43 & 1                  & 7.33 & 5.12  & 0.7    &      &      &        \\
    $(7,8,\thenBr)$   & 2        & 37       & 30   & 0.81      & 8  & 8  & 1                & 12 & 13 & 1.08               & 3.75 & 2.31  & 0.62   & -  & 0.66 & -   \\
    $(10,11,\thenBr)$ & 3        & \un{200} & 167  & 0.84      & 11 & 10 & 0.91             & 10 & 11 & 1.1                & 16.7 & 15.18 & 0.91   & 0.88 & 0.96 & -   \\
    $(10,14,\elseBr)$ & 3        & 25       & 21   & 0.84      & 11 & 11 & 1                & 19 & 18 & 0.95               & 1.91 & 1.17  & 0.61   & - & - & -   \\

@@

    \multicolumn{2}{l|}{\textbf{newGame}*}   

@@

    $(6,7,\thenBr)$   & 2        & 16       & 12   & 0.75      & 9  & 7  & 0.78             & 8  & 8  & 1                  & 1.71 & 1.5   & 0.88   & 0.64 & 0.65 & -  \\

@@

    \multicolumn{2}{l|}{\textbf{revealAll}*}  

@@

    $(2,3,\inFor)$    & 1        & 25       & 20   & 0.8       & 24 & 24 & 1                & 24 & 27 & 1.13               & 0.83 & 0.74  & 0.89   & - & - & -  \\
    $(4,5,\inFor)$    & 2        & 35       & 30   & 0.86      & 20 & 20 & 1                & 23 & 26 & 1.13               & 1.5  & 1.15  & 0.77   & 0.62 & -   &  0.37  \\

@@

\multicolumn{2}{l|}{\textbf{shuffleBoard}*}   

@@

    $(13,14,\thenBr)$ & 3        & 5        & 10   & 2         & 5  & 9  & 1.8              & 6  & 10 & 1.67               & 1.11 & 1     & 0.9    & - & - & -  \\
    $(17,18,\thenBr)$ & 3        & 5        & 10   & 2         & 5  & 10 & 2                & 6  & 11 & 1.83               & 1    & 0.91  & 0.91   & - & - & -   \\
\multicolumn{2}{l|}{\textbf{toggleInfo}*}     
                                 & 6        & 6    & 1         & 7  & 7 & 1                 & 9 & 6   & 0.66               & 0.86  & 1     & 1.17  &    &      &       \\
    $(2,3,\thenBr)$   & 1        & 2        & 2    & 1         & 2  & 2 & 1                 & 2 & 1   & 0.5                & 1     & 2     & 2     & - & - & -  \\
    $(6,7,\thenBr)$   & 1        & 2        & 2    & 1         & 3  & 3 & 1                 & 5 & 3   & 0.6                & 0.67  & 0.67  & 1     & 0.37 & 0.36 & -  \\
\multicolumn{2}{l|}{\textbf{isValidCard}}        
                                 & 1001     & 514  & 0.51      & 21 & 8 & 0.38              & 21 & 10 & 0.48               & 64.25 & 51.4  & 0.8    &   &   &       \\
    $(3,6,\elseBr)$   & 1        & \un{200} & 103  & 0.52      & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 51.5  & 51.5  & 1      & 1 & 1 & -   \\
    $(7,8,\inFor)$    & 1        & \un{200} & 103  & 0.52      & 4  & 1 & 0.25              & 4  & 2  & 0.5                & 103   & 51.5  & 0.5    & 1 & 1 & -  \\
    $(10,11,\thenBr)$ & 2        & \un{200} & 102  & 0.51      & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 51    & 51    & 1      & 1 & 1 & -  \\
    $(10,13,\elseBr)$ & 2        & \un{200} & 106  & 0.53      & 4  & 1 & 0.25              & 4  & 2  & 0.5                & 106   & 53    & 0.5    & 1 & 1 & -  \\
    $(14,15,\inFor)$  & 1        & \un{200} & 100  & 0.5       & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 50    & 50    & 1      & 1 & 1 & -  \\

@@

\multicolumn{2}{l|}{\textbf{isValidVISA}}        
                                 & 201      & 95   & 0.47      & 8  & 3 & 0.38              & 8  & 2  & 0.25               & 31.67 & 47.5  & 1.5    &   &   &       \\
    $(2,3,\thenBr)$   & 1        & \un{200} & 95   & 0.48      & 7  & 3 & 0.43              & 7  & 2  & 0.29               & 31.67 & 47.5  & 1.5    & 1 & 1 & -  \\
\multicolumn{2}{l|}{\textbf{initShields}*}    
                                 & 6        & 5    & 0.83      & 6  & 5 & 0.83              & 6  & 3  & 0.5                & 1      & 1.67 & 1.67   &      &      &       \\
    $(2,3,\inFor)$    & 1        & 6        & 5    & 0.83      & 6  & 4 & 0.67              & 6  & 3  & 0.5                & 1.25   & 1.67 & 1.33   & 0.83 & 0.84 & -  \\
\multicolumn{2}{l|}{\textbf{brickJiggler}*}   
                                 & 7        & 8    & 1.14      & 6  & 4 & 0.67              & 4  & 3  & 0.75               & 2      & 2.67 & 1.33   &      &      &       \\
    $(2,3,\thenBr)$   & 1        & 6        & 7    & 1.17      & 5  & 3 & 0.6               & 3  & 2  & 0.67               & 2.33   & 3.5  & 1.5    & 0.83 & 0.85 & -  \\

@@

\multicolumn{2}{l|}{\textbf{doPaddlePower}*}  
                                 & 19       & 15   & 0.79      & 204  & 140 & 0.69          & 25 & 16  & 0.64              & 0.11   & 0.94 & 8.75   &       &      &      \\
    $(10,11,\thenBr)$ & 1        & 16       & 12   & 0.75      & \un{200} & 136 & 0.68      & 22 & 13  & 0.59              & 0.09   & 0.92 & 10.46  &  0.02 & - & 0.94 \\

@@

\multicolumn{2}{l|}{\textbf{initBricks}*}     
                                 & 1418     & 2379 & 1.68      & 593  & 474 & 0.8           & 422 & 415 & 0.98             & 5.02   & 5.73  & 1.14   &      &      &       \\
    $(6,7,\thenBr)$   & 1        & 2        & 3    & 1.5       & 5    & 4   & 0.8           & 3   & 3   & 1                & 0.75   & 1     & 1.33   & - & -  & -   \\
    $(6,10,\elseBr)$  & 1        & 15       & 23   & 1.53      & 6    & 6   & 1             & 6   & 6   & 1                & 3.83   & 3.83  & 1      & 0.87 & 0.83 & -   \\
    $(11,12,\thenBr)$ & 2        & \un{200} & 317  & 1.59      & 14   & 12  & 0.86          & 17  & 15  & 0.88             & 26.41  & 21.13 & 0.8    & 0.93 & 0.91 & -  \\
    $(11,15,\elseBr)$ & 2        & 18       & 30   & 1.67      & 6    & 6   & 1             & 6   & 6   & 1                & 5      & 5     & 1      & 0.89 & 0.86 & -  \\
    $(16,17,\thenBr)$ & 3        & \un{200} & 324  & 1.62      & 17   & 14  & 0.82          & 17  & 16  & 0.94             & 23.14  & 20.25 & 0.88   & 0.96 & 0.96 & -  \\
    $(16,20,\elseBr)$ & 3        & 25       & 40   & 1.6       & 7    & 7   & 1             & 8   & 7   & 0.88             & 5.71   & 5.71  & 1      & 0.89 & 0.86 & -  \\
    $(21,22,\thenBr)$ & 4        & \un{200} & 310  & 1.55      & 14   & 13  & 0.93          & 17  & 17  & 1                & 23.85  & 18.24 & 0.76   & 0.94 & 0.9  & 0.36  \\
    $(21,25,\elseBr)$ & 4        & 26       & 41   & 1.58      & 7    & 7   & 1             & 8   & 7   & 0.88             & 5.86   & 5.86  & 1      & 0.94 & 0.87 & -  \\
    $(29,30,\thenBr)$ & 1        & \un{200} & 330  & 1.65      & 66   & 58  & 0.88          & 74  & 70  & 0.95             & 5.69   & 4.71  & 0.83   & 0.82 & 0.88 & -   \\
    $(29,37,\elseBr)$ & 1        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & - & - & -  \\
    $(38,39,\thenBr)$ & 2        & 185      & 328  & 1.77      & 85   & 67  & 0.79          & 48  & 44  & 0.92             & 4.9    & 7.45  & 1.52   & 0.87 & 0.88 & -  \\
    $(38,46,\elseBr)$ & 2        & 2        & 4    & 2         & 3    & 4   & 1.33          & 3   & 4   & 1.33             & 1      & 1     & 1      & 0.64 & - & -  \\
    $(47,48,\thenBr)$ & 3        & 187      & 336  & 1.8       & \un{200} & 141 & 0.7       & 127 & 131 & 1.03             & 2.38   & 2.56  & 1.08   & 0.8  & 0.8  & -  \\
    $(47,55,\elseBr)$ & 3        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & 0.66 & 0.61 & -  \\
    $(56,57,\thenBr)$ & 4        & 109      & 198  & 1.82      & 50   & 43  & 0.86          & 49  & 47  & 0.96             & 4.6    & 4.21  & 0.91   & 0.76 & 0.75 & -   \\
    $(56,64,\elseBr)$ & 4        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & 0.64 & 0.61 & -  \\
    $(69,70,\thenBr)$ & 1        & 2        & 4    & 2         & 3    & 4   & 1.33          & 3   & 4   & 1.33             & 1      & 1     & 1      & - & - & -  \\
    $(69,71,\elseBr)$ & 1        & 41       & 81   & 1.98      & 95   & 84  & 0.88          & 27  & 26  & 0.96             & 0.96   & 3.12  & 3.23   & - & 0.68 & 0.61  \\
    \multicolumn{2}{l|}{\textbf{do\_draw}}       
                                 & 268      & 625  & 2.33      & 383  & 1295 & 3.38         & 124 & 334 & 2.69             & 0.48   & 1.87  & 3.88   &      &      &       \\
    $(6,7,\thenBr)$   & 1        & 8        & 19   & 2.38      & 6    & 25   & 4.1          & 7   & 20  & 2.86             & 0.76   & 0.95  & 1.25   & - & -  &  0.62 \\
    $(8,9,\thenBr)$   & 2        & 10       & 23   & 2.3       & 6    & 17   & 2.83         & 7   & 21  & 3                & 1.35   & 1.1   & 0.81   & 0.63 & 0.62 &  - \\
    $(8,11,\elseBr)$  & 2        & 144      & 343  & 2.39      & 17   & 51   & 3            & 19  & 57  & 3                & 6.73   & 6.02  & 0.89   & 0.91 & 0.91 &  - \\
    $(44,45,\thenBr)$ & 1        & 57       & 144  & 2.5       & \un{200} & 681  & 3.4      & 40  & 111 & 2.78             & 0.21   & 1.3   & 6.14   & 0.16 & - &  0.89 \\
    $(48,49,\thenBr)$ & 1        & 26       & 68   & 2.61      & 137  & 492  & 3.59         & 34  & 97  & 2.85             & 0.14   & 0.7   & 5.07   & 0.24 & - &  0.74 \\
\multicolumn{2}{l|}{\textbf{prob\_gamma}}        
                                 & 2006     & 710  & 0.35      & 163 & 84   & 0.52          & 162 & 81  & 0.5              & 8.45   & 8.77  & 1.04   &  &   &        \\
    $(4,5,\thenBr)$   & 1        & \un{200} & 71   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 71     & 71    & 1      & 1 & 1 &  -  \\

>>>>

\documentclass[sigconf,review, anonymous]{acmart}

\usepackage{tablefootnote}
\usepackage{syntax}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{booktabs} % For formal tables
\usepackage{tikz}
\usetikzlibrary{arrows,shadows,positioning,decorations.pathmorphing}
\usepackage{pgf-umlsd}
\usepackage{tikz-uml}
\usepackage{hyperref}
\usepackage{upquote}
\usepackage{listings}
\usepackage{lsthaskell}
\usepackage{xspace}
\usepackage{mdframed}
\usepackage{algorithmic}
\usepackage{longtable}
\usepackage{subcaption}
\usepackage{pgfplots}
\pgfplotsset{compat=newest}
\usepackage[titlenotnumbered, linesnumbered, ruled]{algorithm2e} % language for algorithm description
\hypersetup{
  colorlinks   = true, %Colours links instead of ugly boxes
  urlcolor     = blue, %Colour for external hyperlinks
  linkcolor    = red, %Colour of internal links
  citecolor    = green %Colour of citations
}

@@

\newcommand{\Server}{\emph{Server}\xspace}
\newcommand{\Client}{\emph{Client}\xspace}
\newcommand{\User}{\emph{User}\xspace}
\newcommand{\Validator}{\emph{Validator}\xspace}
\newcommand{\thenBr}{\text{then}}
\newcommand{\elseBr}{\text{else}}
\newcommand{\inFor}{\text{inFor}}
\newcommand{\inWhile}{\text{while}}
\newcommand{\un}[1]{\underline{#1}}
\newcommand{\Random}{\mathbb{R}}
\newcommand{\Genetic}{\mathbb{G}}
\newcommand{\RGenetic}{\mathbb{G}_{10}}

@@

%Conference
\acmConference[ISSTA 2018]{ACM SIGSOFT International Symposium on Software Testing and Analysis}{16-22 July, 2018}{Amsterdam, The Netherlands}
\acmYear{1997}
\copyrightyear{2016}

@@

\author{Alexander Elyasov}
\affiliation{%
  \institution{Utrecht University, The Netherlands} 
}
\email{a.elyasov@uu.nl}

\author{Wishnu Prasetya}
\affiliation{%
  \institution{Utrecht University, The Netherlands}
}
\email{s.w.b.prasetya@uu.nl}

\author{Jurriaan Hage}
\affiliation{%
  \institution{Utrecht University, The Netherlands}
  \country{The Netherlands} 
}
\email{j.hage@uu.nl}

@@

data Tag = HTML | HEAD | BODY | ...
type Context = CFlow | CMetadata | ...
data HtmlState = |c \label{ref.HtmlState.begin} |c
  HtmlState { depth    :: Int,           degree  :: Int    
             , ctx     :: Stack Context, tagFreq :: [(Int, Tag)] 
             , tags    :: [Tag],         ids     :: [String]
             , classes :: [String] } |c \label{ref.HtmlState.end} |c
type GenState s = StateT s Gen |c \label{ref.GenState} |c
type GenHtmlState = GenState HtmlState Html |c \label{ref.GenHtmlState} |c
  \end{haskell}
  \caption{The \texttt{Arbitrary} instance for the \texttt{Html} data type}
  \label{fig.html.arb.def}
\end{figure}

@@

\begin{table}
  \caption{Genetic Algorithm Configurations}
  \label{tbl.gen.config}
    \scriptsize
  \begin{tabular}{l|r|r|r}
    \toprule
    \textbf{Parameter Name} &$\Random$&$\Genetic$ &$\RGenetic$ \\
    \hline
    Population size                   & 50  & 50  & 50  \\
    Archive size                      & 1   & 25  & 25  \\
    Maximum number of generations     & 200 & 200 & 200 \\
    Crossover rate                    & 0   & 0.5 & 0.5 \\
    Mutation rate                     & 0   & 0.5 & 0.5 \\
    History window size               & -   & -   & 10  \\
    \bottomrule
  \end{tabular}
\end{table}

@@

For the sake of space, we chose to exclude from the follow up presentation the branches and functions which coverage time was less than two seconds. In all those cases, the three algorithms studied here have shown equally good results by finding a solution within the first iteration --- random generation. This left us with only 7 case studies contributing to the total number of 14 functions  shown in~Table~\ref{tbl.case.studies}. For each function, we reported the following software metrics\footnote{\url{http://jsmeter.info/} is the tool used for measuring JS code statistics}: lines of code~(\textbf{LOC}), number of branches~(\textbf{BR}), depth~(\textbf{D}), and cyclomatic complexity~(\textbf{CC}). The four rightmost columns \textbf{DOM}, \textbf{id}, \textbf{tag} and \textbf{class} indicate if the function manipulate with \emph{dom}, \emph{id}, \emph{tag} or \emph{class} respectively. To answer the research questions posed in the beginning of Section~\ref{sec.evaluation}, we evaluated our test generation framework on the aforementioned case studies with the results presented in Section~\ref{sub.sec.eval.results}.

@@

\setlength\tabcolsep{.98pt}

@@

  \caption{Branch coverage statistics for three variations of the JS test generation framework}

@@

    \begin{tabular}{l|rrr|rrr|rrr|rrr|rrr}

@@

      \multirow{2}{*}{\textbf{NAME}} &   \multicolumn{3}{c|}{$m_{\Random}$} & \multicolumn{3}{c|}{$m_{\Genetic}$} & \multicolumn{3}{c|}{$m_{\RGenetic}$} & \multirow{2}{*}{$\frac{t_{\Random}}{t_{\Genetic}}$} &  \multirow{2}{*}{$\frac{t_{\Random}}{t_{\RGenetic}}$} & \multirow{2}{*}{$\frac{t_{\Genetic}}{t_{\RGenetic}}$}   & \multirow{2}{*}{\hfil $_{\Genetic}^{\Random}$} &  \multirow{2}{*}{\hfil $_{\RGenetic}^{\Random}$} & \multirow{2}{*}{\hfil $_{\RGenetic}^{\Genetic}$} \\
      \cline{2-10} % \!:\!
                             & $i$      & $t$  & $t/i$     & $i$& $t$&$t/i$             &$i$ &$t$ &$t/i$               &      &       &        &      &       &      \\
      \midrule
    \textbf{helpMe}*         & 218      & 270  & 1.24      & 61 & 47 & 0.77             & 62 & 56 & 0.9                & 5.74 & 4.82  & 0.84   &      &      &       \\
    $(3,4,\inFor)$           & 4        & 4    & 1         & 5  & 3  & 0.6              & 8  & 6  & 0.75               & 1.33 & 0.67  & 0.5    & - & 0.39 & 0.37  \\
    $(5,6,\thenBr)$          & 4        & 5    & 1.25      & 8  & 6  & 0.75             & 7  & 5  & 0.71               & 0.83 & 1     & 1.2    & - & -  & -  \\
    $(5,15,\elseBr)$         & 121      & 156  & 1.29      & 24 & 21 & 0.86             & 23 & 24 & 1.04               & 7.43 & 6.5   & 0.88   & 0.87 & 0.86 & -  \\
    $(9,10,\thenBr)$         & 85       & 101  & 1.19      & 18 & 14 & 0.78             & 19 & 17 & 0.89               & 7.21 & 5.94  & 0.82   & 0.98 & 0.95 & -  \\
    $(9,14,\elseBr)$         & 4        & 4    & 1         & 6  & 4  & 0.67             & 5  & 4  & 0.8                & 1    & 1     & 1      & - & - & -  \\

@@

    \textbf{isGameFinished}* & 264      & 220  & 0.83      & 32 & 30 & 0.94             & 43 & 43 & 1                  & 7.33 & 5.12  & 0.7    &      &      &        \\
    $(7,8,\thenBr)$          & 37       & 30   & 0.81      & 8  & 8  & 1                & 12 & 13 & 1.08               & 3.75 & 2.31  & 0.62   & -  & 0.66 & -   \\
    $(10,11,\thenBr)$        & \un{200} & 167  & 0.84      & 11 & 10 & 0.91             & 10 & 11 & 1.1                & 16.7 & 15.18 & 0.91   & 0.88 & 0.96 & -   \\
    $(10,14,\elseBr)$        & 25       & 21   & 0.84      & 11 & 11 & 1                & 19 & 18 & 0.95               & 1.91 & 1.17  & 0.61   & - & - & -   \\

@@

    \textbf{newGame}*   

@@

    $(6,7,\thenBr)$          & 16       & 12   & 0.75      & 9  & 7  & 0.78             & 8  & 8  & 1                  & 1.71 & 1.5   & 0.88   & 0.64 & 0.65 & -  \\

@@

    \textbf{revealAll}*  

@@

    $(2,3,\inFor)$           & 25       & 20   & 0.8       & 24 & 24 & 1                & 24 & 27 & 1.13               & 0.83 & 0.74  & 0.89   & - & - & -  \\
    $(4,5,\inFor)$           & 35       & 30   & 0.86      & 20 & 20 & 1                & 23 & 26 & 1.13               & 1.5  & 1.15  & 0.77   & 0.62 & -   &  0.37  \\

@@

    \textbf{shuffleBoard}*   

@@

    $(13,14,\thenBr)$        & 5        & 10   & 2         & 5  & 9  & 1.8              & 6  & 10 & 1.67               & 1.11 & 1     & 0.9    & - & - & -  \\
    $(17,18,\thenBr)$        & 5        & 10   & 2         & 5  & 10 & 2                & 6  & 11 & 1.83               & 1    & 0.91  & 0.91   & - & - & -   \\

@@

   \textbf{toggleInfo}*      & 6        & 6    & 1         & 7  & 7 & 1                 & 9 & 6   & 0.66               & 0.86  & 1     & 1.17  &    &      &       \\
    $(6,7,\thenBr)$          & 2        & 2    & 1         & 3  & 3 & 1                 & 5 & 3   & 0.6                & 0.67  & 0.67  & 1     & 0.37 & 0.36 & -  \\

@@

   \textbf{isValidCard}      & 1001     & 514  & 0.51      & 21 & 8 & 0.38              & 21 & 10 & 0.48               & 64.25 & 51.4  & 0.8    &   &   &       \\
    $(3,6,\elseBr)$          & \un{200} & 103  & 0.52      & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 51.5  & 51.5  & 1      & 1 & 1 & -   \\
    $(7,8,\inFor)$           & \un{200} & 103  & 0.52      & 4  & 1 & 0.25              & 4  & 2  & 0.5                & 103   & 51.5  & 0.5    & 1 & 1 & -  \\
    $(10,11,\thenBr)$        & \un{200} & 102  & 0.51      & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 51    & 51    & 1      & 1 & 1 & -  \\
    $(10,13,\elseBr)$        & \un{200} & 106  & 0.53      & 4  & 1 & 0.25              & 4  & 2  & 0.5                & 106   & 53    & 0.5    & 1 & 1 & -  \\
    $(14,15,\inFor)$         & \un{200} & 100  & 0.5       & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 50    & 50    & 1      & 1 & 1 & -  \\

@@

   \textbf{isValidVISA}      & 201      & 95   & 0.47      & 8  & 3 & 0.38              & 8  & 2  & 0.25               & 31.67 & 47.5  & 1.5    &   &   &       \\
    $(2,3,\thenBr)$          & \un{200} & 95   & 0.48      & 7  & 3 & 0.43              & 7  & 2  & 0.29               & 31.67 & 47.5  & 1.5    & 1 & 1 & -  \\
   \textbf{initShields}*     & 6        & 5    & 0.83      & 6  & 5 & 0.83              & 6  & 3  & 0.5                & 1      & 1.67 & 1.67   &      &      &       \\
    $(2,3,\inFor)$           & 6        & 5    & 0.83      & 6  & 4 & 0.67              & 6  & 3  & 0.5                & 1.25   & 1.67 & 1.33   & 0.83 & 0.84 & -  \\
   \textbf{brickJiggler}*    & 7        & 8    & 1.14      & 6  & 4 & 0.67              & 4  & 3  & 0.75               & 2      & 2.67 & 1.33   &      &      &       \\
    $(2,3,\thenBr)$          & 6        & 7    & 1.17      & 5  & 3 & 0.6               & 3  & 2  & 0.67               & 2.33   & 3.5  & 1.5    & 0.83 & 0.85 & -  \\
   \textbf{doPaddlePower}*   & 19       & 15   & 0.79      & 204  & 140 & 0.69          & 25 & 16  & 0.64              & 0.11   & 0.94 & 8.75   &       &      &      \\
    $(10,11,\thenBr)$        & 16       & 12   & 0.75      & \un{200} & 136 & 0.68      & 22 & 13  & 0.59              & 0.09   & 0.92 & 10.46  &  0.02 & - & 0.94 \\
   \textbf{initBricks}*      & 1418     & 2379 & 1.68      & 593  & 474 & 0.8           & 422 & 415 & 0.98             & 5.02   & 5.73  & 1.14   &      &      &       \\
    $(6,7,\thenBr)$          & 2        & 3    & 1.5       & 5    & 4   & 0.8           & 3   & 3   & 1                & 0.75   & 1     & 1.33   & - & -  & -   \\
    $(6,10,\elseBr)$         & 15       & 23   & 1.53      & 6    & 6   & 1             & 6   & 6   & 1                & 3.83   & 3.83  & 1      & 0.87 & 0.83 & -   \\
    $(11,12,\thenBr)$        & \un{200} & 317  & 1.59      & 14   & 12  & 0.86          & 17  & 15  & 0.88             & 26.41  & 21.13 & 0.8    & 0.93 & 0.91 & -  \\
    $(11,15,\elseBr)$        & 18       & 30   & 1.67      & 6    & 6   & 1             & 6   & 6   & 1                & 5      & 5     & 1      & 0.89 & 0.86 & -  \\
    $(16,17,\thenBr)$        & \un{200} & 324  & 1.62      & 17   & 14  & 0.82          & 17  & 16  & 0.94             & 23.14  & 20.25 & 0.88   & 0.96 & 0.96 & -  \\
    $(16,20,\elseBr)$        & 25       & 40   & 1.6       & 7    & 7   & 1             & 8   & 7   & 0.88             & 5.71   & 5.71  & 1      & 0.89 & 0.86 & -  \\
    $(21,22,\thenBr)$        & \un{200} & 310  & 1.55      & 14   & 13  & 0.93          & 17  & 17  & 1                & 23.85  & 18.24 & 0.76   & 0.94 & 0.9  & 0.36  \\
    $(21,25,\elseBr)$        & 26       & 41   & 1.58      & 7    & 7   & 1             & 8   & 7   & 0.88             & 5.86   & 5.86  & 1      & 0.94 & 0.87 & -  \\
    $(29,30,\thenBr)$        & \un{200} & 330  & 1.65      & 66   & 58  & 0.88          & 74  & 70  & 0.95             & 5.69   & 4.71  & 0.83   & 0.82 & 0.88 & -   \\
    $(29,37,\elseBr)$        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & - & - & -  \\
    $(38,39,\thenBr)$        & 185      & 328  & 1.77      & 85   & 67  & 0.79          & 48  & 44  & 0.92             & 4.9    & 7.45  & 1.52   & 0.87 & 0.88 & -  \\
    $(38,46,\elseBr)$        & 2        & 4    & 2         & 3    & 4   & 1.33          & 3   & 4   & 1.33             & 1      & 1     & 1      & 0.64 & - & -  \\
    $(47,48,\thenBr)$        & 187      & 336  & 1.8       & \un{200} & 141 & 0.7       & 127 & 131 & 1.03             & 2.38   & 2.56  & 1.08   & 0.8  & 0.8  & -  \\
    $(47,55,\elseBr)$        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & 0.66 & 0.61 & -  \\
    $(56,57,\thenBr)$        & 109      & 198  & 1.82      & 50   & 43  & 0.86          & 49  & 47  & 0.96             & 4.6    & 4.21  & 0.91   & 0.76 & 0.75 & -   \\
    $(56,64,\elseBr)$        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & 0.64 & 0.61 & -  \\
    $(69,70,\thenBr)$        & 2        & 4    & 2         & 3    & 4   & 1.33          & 3   & 4   & 1.33             & 1      & 1     & 1      & - & - & -  \\
    $(69,71,\elseBr)$        & 41       & 81   & 1.98      & 95   & 84  & 0.88          & 27  & 26  & 0.96             & 0.96   & 3.12  & 3.23   & - & 0.68 & 0.61  \\
    \textbf{do\_draw}        & 268      & 625  & 2.33      & 383  & 1295 & 3.38         & 124 & 334 & 2.69             & 0.48   & 1.87  & 3.88   &      &      &       \\
    $(6,7,\thenBr)$          & 8        & 19   & 2.38      & 6    & 25   & 4.1          & 7   & 20  & 2.86             & 0.76   & 0.95  & 1.25   & - & -  &  0.62 \\
